Methods for Large Scale Learning to Rank

### 2014-03-24 report/Chapters/BenchmarkResults.tex
begin cross dataset comparison

>>>>

\subsection{AOL}
TODO: AOL dataset beschrijven \cite{Pass2006}.

\section{comparing Learning-to-Rank models across datasets}
\begin{table}[!h]
\begin{tabular}{l|l|l}
Benchmark & Paper & \# of forward references \\
\hline
LETOR 1.0 \& 2.0 & Liu et al. \cite{Liu2007b} & 307\\
LETOR 3.0 & Qin et al. \cite{Qin2010} & 105\\
Yahoo! Learning to Rank Challenge & Chapelle et al. \cite{Chapelle2011a} & 102 forward references\\
AOL dataset & Pass et al. \cite{Pass2006} & 339\\
WCL2R & Alc{\^a}ntara et al. \cite{Alcantara2010} & 2\\
\end{tabular}
\caption{Forward references of Learning-to-Rank benchmark papers}
\label{tbl:ltr_benchmark_forref}
\end{table}
Google scholar search results for benchmark data sets without a release/overview paper.
\begin{table}
\begin{tabular}{l|l}
Benchmark & Google scholar search results \\
\hline
LETOR 4.0 & 75 results \\
MSLR-web10k & 16 results \\
MSLR-web30k & 15 results \\
Yandex Internet Mathematics Competition & 1 result \\ 
\end{tabular}
\caption{Google scholar search results for Learning-to-Rank benchmarks}
\label{tbl:ltr_benchmark_searchres}
\end{table}
